### 2020-04-30 thesis/thesis.tex
added thesis files but not building yet.
working on getting thesis to compile. Still some encoding character error.
needed to turn a unicode symbol into unicode.
added in final chapters including author contributions.

\usepackage[hypertexnames=false]{hyperref}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Pommerenck Thesis},    % title
    pdfauthor={Jordan K. Pommerenck},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1, key2, key3}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links (change box color with linkbordercolor)
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

@@

\usepackage[left=1.5in,right=1in,top=1in,bottom=1in,includefoot,heightrounded]{geometry}
\usepackage[pagestyles]{titlesec}

\sethead{\itshape\chaptername\thechapter}{}{\itshape\chaptertitle}
\titleformat{\chapter}[display]{\normalfont\bfseries\Large\centering}{}{18pt}{\Large}
\titlespacing{\chapter}{0pt}{0pt}{1cm}

\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
% differential and partials package
\usepackage[thinc]{esdiff}
\usepackage{physics}
\newcommand{\D}[1]{\text{d}#1}
% the nth superscript package
\usepackage[super]{nth}

@@

\addbibresource{thesis.bib}

@@

% \usepackage{color}
% \newcommand{\red}[1]{{\bf \color{red} #1}}
% \newcommand{\green}[1]{{\bf \color{green} #1}}

% \newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
% \newcommand{\jpsays}[1]{{\color{red} [\red{Jordan:} \emph{#1}]}}

@@

@@

\input{chapter-1}
%\input{Chapters/Chapter2_Files/sad.tex}
%\input{Chapters/Chapter3_Files/ising.tex}

%\chapter{Conclusion}
%\input{Chapters/chapter06}

>>>>

\usepackage[hypertexnames=false]{hyperref}
\hypersetup{
    unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Pommerenck Thesis},    % title
    pdfauthor={Jordan K. Pommerenck},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={flat-histogram, Monte-Carlo, Thesis}, % list of keywords
    pdfnewwindow=true,      % links in new PDF window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links (change box color with linkbordercolor)
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

@@

\usepackage[left=1.5in,right=1in,top=1in,bottom=1in,includefoot,heightrounded]{geometry}
%\usepackage[pagestyles]{titlesec}

%\sethead{\itshape\chaptername\thechapter}{}{\itshape\chaptertitle}
%\titleformat{\chapter}[display]{\normalfont\bfseries\Large\centering}{}{18pt}{\Large}
%\titlespacing{\chapter}{0pt}{0pt}{1cm}

%\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}
% differential and partials package
\usepackage[thinc]{esdiff}
\usepackage{physics}
\newcommand{\D}[1]{\text{d}#1}
% the nth superscript package
\usepackage[super]{nth}

@@

%\addbibresource{thesis.bib}

@@

\usepackage{color}
\newcommand{\red}[1]{{\bf \color{red} #1}}
\newcommand{\green}[1]{{\bf \color{green} #1}}

\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\jpsays}[1]{{\color{red} [\red{Jordan:} \emph{#1}]}}

@@

% THE BIBLIOGRAPHY NEEDS TO COME BEFORE ALL OF THE CHAPTERS
\bibliography{thesis}

@@

% introduction
\input{chapter-1}
% sq-well paper
\input{chapter-2}
% ising paper
\input{chapter-3}
% gas-adsorption paper
\input{chapter-4}
% general conclusion linking all manuscripts
\input{chapter-5}
